Blame and Coercion: Together Again for the Second Time

### 2019-10-03 paper.tex
static semantics of blame calculus

\begin{figure}
	\[
	\begin{array}{lclr}
	\stxrule{S,T}{types}{
		\star \mid{}
		P
	}
	\stxrule{P,Q}{pre-types}{
		\iota \mid{}
		T_1 \rightarrow T_2 \mid{}
		T_1 \times T_2 \mid{}
		T_1 \plus T_2 \mid{}
	}
%	\stxrule{x,y,z}{variables}{\dots}
%	\stxrule{l}{labels}{\dots}
%	\stxrule{k}{constants}{sole}
	\stxrule{e}{terms}{
		x \mid{}
		k \mid{}
		\lambda^{S\rightarrow{}T}x.t \mid{}
		e_1 \; e_2 \mid{}
		\langle T \Leftarrow^l S \rangle t \mid{}
		\mathtt{blame} \; l
	}
	\stxrulecont{
		\mathtt{cons}\; e_1 \; e_2 \mid{}
		\mathtt{car}\; e \mid{}
		\mathtt{cdr}\; t
	}
	\stxrulecont{
		\mathtt{inl} \; e \mid{}
		\mathtt{inr} \; e \mid{}
		\mathtt{case}\; e_1 \; e_2 \; e_3
	}
	\stxrule{o}{observations}{
		k \mid{}
		\mathtt{fun}\mid{}
		\mathtt{cons}\mid{}
		\mathtt{inl}\mid{}
		\mathtt{inr}\mid{}
		\mathtt{blame}\; l
	}
	\end{array}
	\]

@@

Let $ e $ ranges over terms. Unlike $ \mathtt{STLC+} $, we annotate the 
co-domain of lambda abstractions explicitly and add casts and blames.

@@

>>>>

\begin{figure}
	\[
	\begin{array}{lclr}
	\stxrule{S,T}{types}{
		\star \mid{}
		P
	}
	\stxrule{P,Q}{pre-types}{
		\iota \mid{}
		T_1 \rightarrow T_2 \mid{}
		T_1 \times T_2 \mid{}
		T_1 \plus T_2 \mid{}
	}
%	\stxrule{x,y,z}{variables}{\dots}
%	\stxrule{l}{labels}{\dots}
%	\stxrule{k}{constants}{sole}
	\stxrule{e}{terms}{
		x \mid{}
		\mathtt{tt} \mid{}
		\lambda^{S\rightarrow{}T}x.t \mid{}
		e_1 \; e_2 \mid{}
		\langle T \Leftarrow^l S \rangle t \mid{}
		\mathtt{blame} \; l
	}
	\stxrulecont{
		\mathtt{cons}\; e_1 \; e_2 \mid{}
		\mathtt{car}\; e \mid{}
		\mathtt{cdr}\; t
	}
	\stxrulecont{
		\mathtt{inl} \; e \mid{}
		\mathtt{inr} \; e \mid{}
		\mathtt{case}\; e_1 \; e_2 \; e_3
	}
	\stxrule{o}{observations}{
		\mathtt{tt} \mid{}
		\mathtt{fun}\mid{}
		\mathtt{cons}\mid{}
		\mathtt{inl}\mid{}
		\mathtt{inr}\mid{}
		\mathtt{blame}\; l
	}
	\end{array}
	\]

@@

Let $ e $ ranges over terms. Unlike $ \mathtt{STLC+} $, we annotate the 
co-domain of lambda abstractions explicitly. Besides, we add casts and blames.

Let $ o $ ranges over observations.

Now let's move to the dynamic semantics.

@@

We describe the dynamic semantics of Blame Calculus with the CEK machine 
(\citet{felleisen1986control}).
